\LARGE \bf ***

### 2020-09-22 icra-2021.tex
some fixes until 'position in space and guidance action'

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
The algorithm inspires notably by the technique of coupling the energy due to the computations performed and trajectory traveled, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

The proposed algorithm adapts the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. It ideally accounts for a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters. It optimizes TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

@@

The remainder of the paper is organized as follows. A suitable energy model for the path and the computations is showed in Section~\ref{sec:model}. The algorithm that uses the energy model to address dynamic mission planning is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

---
%%%%%%%%%%%%%%%
\section{Model}
\label{sec:model}

The algorithm utilizes the model to estimate the robot's position in space and its energy evolution in time.

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space, with respect to some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using vector field~\cite{de2017guidance}. To define the direction to follow, we use generic continuously differentiable functions TEEs $\varphi:\mathbb{R}^3\rightarrow\mathbb{R}$, a mathematical abstraction representing the desired trajectory (being the function satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the points approaching such trajectory).

The energy evolution $\mathbf{q}\in\mathbb{R}^j$ spent to perform such guidance action is derived using Fourier analysis (the meaning of $j$ will be explained to the reader in Subsection~\ref{sec:energy-model}) and is decomposed in the energy due to the trajectory (TEEs), and the computations (QoS)--an approach that has been adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing craft~\cite{seewald2020mechanical}.

>>>>

Although underrepresented in precision agriculture literature, energy planning algorithms for mobile robots are not a new concept and have been extensively studied, being these correlated to such topics as trajectory generation and path planning. Generally, they account for the energy due to the trajectory, by e.g., maximizing the operation time~\cite{wahab2015energy}, but practically restrict to a narrow class of mobile robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}. In a similar setting, rotorcrafts have been an obvious object of research interest, with algorithms such as energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Conversely, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands of precision agriculture UAVs through a mission-aware perspective.
The technique of coupling the energy due to the computations performed and trajectory traveled inspires notably the algorithm, although such technique being, likewise the others, limited to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, or to the class of mobile robots~\cite{sadrpour2013mission,sadrpour2013experimental}.

The proposed algorithm alters the energy dynamically, defining mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. It ideally accounts for a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) with computationally expensive ROS nodes controlled through ROS parameters. It optimizes TEEs--a mathematical abstraction of the path to follow--and implements the change updating a vector field that converges smoothly to such path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

@@

The remainder of the paper is organized as follows. A suitable model for the energy and position of the UAV is showed in Section~\ref{sec:model}. The algorithm that uses the model and implements the dynamic mission planning is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents a fixed-wing UAV flying in an agricultural scenario showcasing the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

%%%%%%%%%%%%%%%
\section{Model}
\label{sec:model}

The algorithm uses the model to estimate the UAV's position in space and its energy evolution in time.

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t. some inertial navigation frame $\mathcal{O}_W$, a guidance action--which allows the motion along the 3-axis--is built upon the direction to follow and derived using a vector field~\cite{de2017guidance}. Before the guidance action, we need to define the path: a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).

The energy evolution $\mathbf{q}\in\mathbb{R}^j$ is built using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decomposed in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from authors' earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.

\begin{center}\vspace{.2cm}---\emph{from here on work in progress}---\vspace{.6cm}\end{center}
